%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects and  Activity}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Developer and Test} % Affiliation/role
    {} % Organization/group
    {School} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {A Java based Swing Calculator. This calculator was scientific calculator, that could do all ciruclar functions, trignometric fuctions and logarithms in base 10 and base 2. AWT and Swing based design flows were used to do the GUI}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Database Warehousing} % Affiliation/role
    {} % Organization/group
    {School} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {A Java and Mysql based data warehousing. This was done as part of classwork in data mining. The project was to mine wikiepedia pages and report the seasonal pages that underwent maximum edits and thus were classifieds as hotspots. Usage: In predicting news, financial implictions like stock markets.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Developer and Test} % Affiliation/role
    {} % Organization/group
    {School} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Tomcat Server based multiparty game. This game was learning project on deploying server and doing a push notification through server in a simple gambling game.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Developer and Tester} % Affiliation/role
    {} % Organization/group
    {School} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {A custom library for dealing with Big Integer kind of representaion. The project was challenging as it required totally new way of looking at computation model and implenting  that in java.}
      \end{cvitems}
    }

\cventry
    {Developer and Tester in a Team} % Affiliation/role
    {} % Organization/group
    {Partnership} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item { Nasdaq stock guide. This is an ambitious part time project with my cofounder. The project is at cusp of data mining, data prediction, and programming. I am actively contributing to data analysis portion of project. Python and scala}
      \end{cvitems}
    }

\end{cventries}
