%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Staff Software Engineer in Backend } % Job title
    {Xad Inc} % Organization
    {San Francisco, CA} % Location
    {Jul. 2015 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented real time auction server in newer scala framework} 
        \item {Architect engineer in cluster controller subsystem that provided distributed programming model with strong exception gurantees.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Staff Software Engineer in Backend } % Job title
    {Emc Inc} % Organization
    {San Francisco, CA} % Location
    {Jan. 2015 - July. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Data Science and Analytics. A short term work in  breaking ground for incorporating recommneder system in storage usage analytics of content managemnt systems. Created experimental models and studied the suitablilty of approaches.}
      \end{cvitems}
    }



%---------------------------------------------------------
  \cventry
    {Staff Software Engineer in Compiler Optimization } % Job title
    {Synopsys Inc} % Organization
    {San Francisco, CA} % Location
    {Dec. 2012 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Major contribution in feature enhancement and management of optimzer engine of synopsys integrated circuits compiler.}
        \item {Recognized for new optimization goal implementation in the electromagnetic emission constraint optimization problem.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Software Engineer in multimedia serving  systems } % Job title
    {Nuance Inc} % Organization
    {San Francisco, CA} % Location
    {Dec. 2010 - Dec. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Major contribution to bringing up new packet voice distributed processing system offered as SAS. Involved in conceptual design of backend architecture of server systems like load balancing, failsafe architectures.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer in multimedia embedded  systems } % Job title
    {Ditech Inc} % Organization
    {San Francisco, CA} % Location
    {Apr. 2006 - Aug. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Major contribution in design of packet multimedia processing and control system in multi array processor system with colocated cores. The system needed to provide low latency and high bandwidth packet processing solutions to mobile phone networks.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Firmware Engineer in multimedia embedded  systems } % Job title
    {Conexant Inc} % Organization
    {Redbanks, NJ} % Location
    {Apr. 2004 - apr. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Major contribution in implementing signal processing modules in DSL modem processors. Usage of acquistion and statistical techniques to decode data in dsl networks.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer in multimedia embedded  systems } % Job title
    {Ittiam systems Inc} % Organization
    {Bangalore, India} % Location
    {Jul. 2001 - Mar. 2004} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Major contribution in design of real time scheduler and  signal acquistion systems in PowerPC based architectures to implement telephony based modems.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
