%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------  
\cventryOnlyDescription
      {\begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Multi years experience in designing, implementing and maintaining distributed, multi processor and multicore systems for applications serving in an efficient manner while optimizing development velocity and risk.}
	\item {Driven towards bias to action and implementation, experience in early stage startups and used to fast paced delivery and implementation of software projects.}
        \item {Strong background in theoretical and practical approaches to design and implementation of computer based systems in distributed and embedded architectures.}
	\item{Interested in applying logical process of breaking down a complex problem to reasonable level where it can implemented and measured for next iteration.}
	\item {Believer in iterative approaches to reach an unclear goal. Specify, implement, observe, get feedback, generalize and repeat.}
	\item {Languages: Java, Scala, Python, C++, C, Shell.}
	\item {Systems: Linux kernel, Hadoop, MPI platform, Sql Systems, NoSql Systems, Message buses, Amazon AWS.}
	\item {Frameworks: Spring, Play, Flask, Spark, Hadoop.}
	\item {Technologies: Kafka, Redis, RabbitMq, NLTK, NumPy, MySql, MongoDb, Cassandra, Hbase, Excel.}
       \end{cvitems}
      }
%---------------------------------------------------------
\end{cventries}
